Retrofitting Effect Handlers onto OCaml

### 2020-11-03 retro-concurrency.tex
minor edit
Updated the microbenchmarks for comparing stock vs effects: external, callbacks, handler return, handler + raise

\subsection{Retrofitting effect handlers}
\label{sec:req}

@@

\subsection{Requirements}
\label{sec:requirements}

@@

One of our goals(\S\ref{sec:requirements}) is to make this code transparently
asynchronous. We can define effects for performing the I/O operations  and wrap
them up in functions with the same signature as the one from the standard
library:
\begin{lstlisting}
effect In_line : in_channel -> string
effect Out_str : out_channel -> string -> unit
let input_line ic = perform (In_line ic)
let output_string oc = perform (Out_str oc)
\end{lstlisting}

@@

TODO:
\begin{itemize}
\item Aim: |R1| not altered existing code performance too much
\item sandmark macro benchmarks to show sequential performance: 4.10.0+stock, 4.10.0+multicore,
4.10.0+multicore no red-zone/leaf-optimization, 4.10.0+multicore
\item do we want to include some micro-benchmarks focusing on the FFI callstack overhead?
\end{itemize}

>>>>

\subsection{Retrofitting effect handlers}

@@

\subsection{Requirements}
\label{sec:req}

@@

One of our goals(\S\ref{sec:req}) is to make this code transparently
asynchronous. We can define effects for performing the I/O operations  and wrap
them up in functions with the same signature as the one from the standard
library:
\begin{lstlisting}
effect In_line : in_channel -> string
effect Out_str : out_channel -> string -> unit
let input_line ic = perform (In_line ic)
let output_string oc = perform (Out_str oc)
\end{lstlisting}

@@

TODO:
\begin{itemize}
\item Aim: |R1| not altered existing code performance too much
\item micro-benchmarks covering 1M external calls, 1M callbacks, 1M install handler return, 1M install handler + raise; 4.10.0+stock vs 4.10.0+multicore
\item sandmark macro benchmarks to show sequential performance: 4.10.0+stock, 4.10.0+multicore,
4.10.0+multicore no red-zone/leaf-optimization, 4.10.0+multicore
\end{itemize}
